---
title: "README"
author: "Abhishek salape"
date: "12/06/2020"
output: html_document
---
##Assignment Instructions  
1.Code for reading in the dataset and/or processing the data  
2.Histogram of the total number of steps taken each day  
3.Mean and median number of steps taken each day  
4.Time series plot of the average number of steps taken  
5.The 5-minute interval that, on average, contains the maximum number of steps  
6.Code to describe and show a strategy for imputing missing data  
7.Histogram of the total number of steps taken each day after missing values are imputed  
8.Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends  
9.All of the R code needed to reproduce the results (numbers, plots, etc.) in the report  

**STEP 1**  
##code for Reading & Exploring The data 
```{r,echo=TRUE,results='hide'}

setwd("C:/Users/Hp/Documents")
activity <- read.csv("./activity.csv")
head(activity)
str(activity)
dim(activity)
sum(is.na(activity$steps))

  ```
  
**STEP 2**  
##Histogram of the total number of steps taken each day
```{r,echo=TRUE,results='hide'}
  
library(ggplot2)
setwd("C:/Users/Hp/Documents")
activity <- read.csv("./activity.csv")
Q2<-data.frame(tapply(activity$steps,activity$date,sum,na.rm=TRUE))
Q2$date<-rownames(Q2)
rownames(Q2)<-NULL
names(Q2)[[1]]<-"Total Steps"
#Total Steps by date bar chart
png("plot11.png")
ggplot(Q2,aes(y=Q2$`Total Steps`,x=Q2$date))+geom_bar(stat="identity") + ylab("Total Steps")+xlab("Date")+ggtitle("Total Steps by date")
dev.off()

```

**STEP 3**  
##Mean and median number of steps taken each day

```{r,echo=TRUE,results='hide'}
setwd("C:/Users/Hp/Documents")
activity <- read.csv("./activity.csv")
totalStepsByDay<-aggregate(steps~date, activity, sum)
mean(totalStepsByDay$steps)
median(totalStepsByDay$steps)

```
**STEP 4**
##Time series plot of the average number of steps taken  
```{r,echo=TRUE,results='hide'}
averageStepsbyInterval<-aggregate(steps~interval, activity, mean)
png("plot12.png")
with(averageStepsbyInterval, plot(interval, steps, type = "l"))  

```
**STEP 5**  
##Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?  

```{r,echo=TRUE,results='hide'}

averageStepsbyInterval[which.max(averageStepsbyInterval[,2]),1]

```


**STEP 6**









